Reasoning with Language Model is Planning with World Model

### 2024-07-05 nlp-papers/reasoning-via-planning/emnlp2023.tex
deploy: 3dc9494d6b5c6fe6e828db8f0e990c1af8bb5bcf
deploy: 09732c01d7193d9bf0f6a417c56d46d1862db069

\documentclass[11pt]{article}
\usepackage{EMNLP2023}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{listings}
\lstset{
  backgroundcolor=\color{gray!8},
  basicstyle=\ttfamily,
  columns=fullflexible
}
% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{inconsolata}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath, amsfonts, amssymb}

@@

>>>>

\documentclass[11pt]{article}
\usepackage{EMNLP2023}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{listings}
\lstset{
  backgroundcolor=\color{gray!8},
  basicstyle=\ttfamily,
  columns=fullflexible
}
% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont{Ubuntu}
\setmonofont{Ubuntu}
\setsansfont{Ubuntu}
\urlstyle{same}
\usepackage[most]{tcolorbox}
\newtcbox{\roundinlinebox}[1][red]{
    on line,
    arc=7pt,
    colback=#1!10!white,
    colframe=#1!50!white,
    before upper={\rule[-3pt]{0pt}{10pt}},
    boxrule=1pt,
    boxsep=0pt,left=6pt,right=6pt,top=2pt,bottom=2pt
}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{inconsolata}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath, amsfonts, amssymb}

@@

\usepackage{soul}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}

\makeatletter

\newcommand{\defhighlighter}[3][]{%
    \tikzset{every highlighter/.style={color=#2, fill opacity=#3, #1}}%
}

\defhighlighter{yellow}{.5}

\newcommand{\highlight@DoHighlight}{
    \fill [ decoration = {random steps, amplitude=1pt, segment length=15pt}
        , outer sep = -15pt, inner sep = 0pt, decorate
        , every highlighter, this highlighter ]
    ($(begin highlight)+(0,8pt)$) rectangle ($(end highlight)+(0,-3pt)$) ;
}

\newcommand{\highlight@BeginHighlight}{
    \coordinate (begin highlight) at (0,0) ;
}

\newcommand{\highlight@EndHighlight}{
    \coordinate (end highlight) at (0,0) ;
}

\newdimen\highlight@previous
\newdimen\highlight@current

\DeclareRobustCommand*\highlight[1][]{%
    \tikzset{this highlighter/.style={#1}}%
    \SOUL@setup
%
    \def\SOUL@preamble{%
        \begin{tikzpicture}[overlay, remember picture]
            \highlight@BeginHighlight
            \highlight@EndHighlight
        \end{tikzpicture}%
    }%
%
    \def\SOUL@postamble{%
        \begin{tikzpicture}[overlay, remember picture]
            \highlight@EndHighlight
            \highlight@DoHighlight
        \end{tikzpicture}%
    }%
%
    \def\SOUL@everyhyphen{%
        \discretionary{%
            \SOUL@setkern\SOUL@hyphkern
            \SOUL@sethyphenchar
            \tikz[overlay, remember picture] \highlight@EndHighlight ;%
        }{%
        }{%
            \SOUL@setkern\SOUL@charkern
        }%
    }%
%
    \def\SOUL@everyexhyphen##1{%
        \SOUL@setkern\SOUL@hyphkern
        \hbox{##1}%
        \discretionary{%
            \tikz[overlay, remember picture] \highlight@EndHighlight ;%
        }{%
        }{%
            \SOUL@setkern\SOUL@charkern
        }%
    }%
%
    \def\SOUL@everysyllable{%
        \begin{tikzpicture}[overlay, remember picture]
            \path let \p0 = (begin highlight), \p1 = (0,0) in \pgfextra
            \global\highlight@previous=\y0
            \global\highlight@current =\y1
            \endpgfextra (0,0) ;
            \ifdim\highlight@current < \highlight@previous
            \highlight@DoHighlight
            \highlight@BeginHighlight
            \fi
        \end{tikzpicture}%
        \the\SOUL@syllable
        \tikz[overlay, remember picture] \highlight@EndHighlight ;%
    }%
    \SOUL@
}
\makeatother
